Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-23 doc/main_jfm.tex
worked on intro

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a vesicle made of Janus
particles does behave like a vesicle in these flowing conditions.
Furthermore we also show that the hybrid continuum model allows us to
investigate the inter-leaflet slippage and rupture of a bilayer membrane
due to an imposed flow. Finally, we compare a pair of interacting
Janus-vesicles with a continuum model of a pair of vesicles.

>>>>

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a Janus-vesicle behaves like
a vesicle in these flowing conditions. In particular, we show that a
Janus-vesicle undergoes tank-treading in a shear flow and vertical
migration in a channel flow. Furthermore we use the hybrid continuum
model to investigate the inter-leaflet slippage and rupture of a bilayer
membrane due to an imposed flow. Finally, we compare a pair of
interacting Janus-vesicles with a continuum model of a pair of vesicles.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}), which
guarantee that the suspension remains contact-free. These methods do not
introduce stiffness, but potentially expensive nonlinear complementarity
problems must be solved at each time step.  Repulsion-based contact
methods, which we employ, introduce an artificial repulsion force that
increases in strength as two particles approach one another
(\cite{glo-pan-hes-jos-per2001, fen-mic2004, kab-qua-bir2018}). Strong
repulsion forces can introduce numerical stiffness, but with the
presence of the hydrophobic forces, we maintain a contact-free
suspensions with a relatively weak non-stiff repulsive force.
